Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming

### 2023-01-15 paper.Rmd
Sun Jan 15 16:00:05 CET 2023: update-remote.sh

```{bash recompile_results, include=FALSE}

@@

# summarize csv files for full run experiments
/Users/rmn/miniconda3/envs/dataScience/bin/python /Users/rmn/github/master_thesis/data/summarize_csv_files.py

@@

<!-- Overview Table  -->

@@

<!-- Overview Plots  -->

\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/energyCooling_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/bostonHousing_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} \\
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/concrete_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png}
\end{tabular}

>>>>

```{bash recompile_results, include=FALSE, eval=FALSE}

@@

# summarize csv files for full run experiments
/Users/rmn/miniconda3/envs/dataScience/bin/python /Users/rmn/github/master_thesis/data/summarize_data.py

@@

Next I studied the size of solutions based on using a pre-training strategy. Plot X shows the median size of the best solutions aggregated of all benchmark problems for symbolic regression

![Median Solution Size - Symbolic Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_bestSol_size_byGens.png){height=80%}

Table X summarizes the results of the statistical tests.

@@

### 2023-01-15 slides.Rmd
Sun Jan 15 16:00:05 CET 2023: update-remote.sh

```{bash recompile_results, eval=TRUE, include=FALSE}

@@

![Airfoil - Verteilung der finalen Fitness (1HL)](~/masterThesis/master_thesis/img/airfoil_1hl_maxIndSize_fullRun_30gens/final_fit_boxplot.png){height=90%}

@@

\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/energyCooling_2hl_maxIndSize_fullRun_30gens/median_fitness_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/bostonHousing_2hl_maxIndSize_fullRun_30gens/median_fitness_byGens.png} \\
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/median_fitness_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/concrete_2hl_maxIndSize_fullRun_30gens/median_fitness_byGens.png}
\end{tabular}

@@

\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/energyCooling_2hl_maxIndSize_fullRun_30gens/median_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/bostonHousing_2hl_maxIndSize_fullRun_30gens/median_Size_byGens.png} \\
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/median_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/concrete_2hl_maxIndSize_fullRun_30gens/median_Size_byGens.png}
\end{tabular}

@@

\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/energyCooling_2hl_maxIndSize_fullRun_30gens/median_popDiversity_byGens_levOnly.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/bostonHousing_2hl_maxIndSize_fullRun_30gens/median_popDiversity_byGens_levOnly.png} \\
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/median_popDiversity_byGens_levOnly.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/concrete_2hl_maxIndSize_fullRun_30gens/median_popDiversity_byGens_levOnly.png}
\end{tabular}

## Auswertung Populationsdiversität - Symbolische Regression

@@

\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/energyCooling_2hl_maxIndSize_fullRun_30gens/median_epochs_trained_perGen.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/bostonHousing_2hl_maxIndSize_fullRun_30gens/median_epochs_trained_perGen.png} \\
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/median_epochs_trained_perGen.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/concrete_2hl_maxIndSize_fullRun_30gens/median_epochs_trained_perGen.png}
\end{tabular}

>>>>

```{bash recompile_results, eval=FALSE, include=FALSE}

@@

![Airfoil - Verteilung der finalen Fitness (1HL)](~/masterThesis/master_thesis/img/airfoil_1hl_maxIndSize_fullRun_30gens/final_fit_boxplot.png){height=75%}

@@

![Übersicht Median Fitness - Symbolische Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_fitness_byGens.png){height=80%}

@@

![Übersicht Lösungsgröße (Median) - Symbolische Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_bestSol_size_byGens.png){height=80%}

@@

![Übersicht Populationsdiversität (Median) - Symbolische Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_levDistance_byGen.png){height=80%}

## Auswertung Populationsdiversität (Median) - Symbolische Regression

@@

![Übersicht Trainingsepochen pro Generation (Median) - Symbolische Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_epochsTrained.png){height=80%}
